---
title: "interactive_map"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(leaflet)
library(lubridate)
```

```{r, warning = FALSE, message = FALSE}
## load sensor data

sensor_data <- read_csv("Sensor Data.csv")

sensor_data_clean <- sensor_data %>%
  rename(
    time = `Date Time`
  ) %>%
  mutate(time = mdy_hm(time))
```


```{r, warning = FALSE, message = FALSE}
## load meteorological data

weather_data <- read_csv("Meteorological Data.csv")

weather_data_clean <- weather_data %>%
  rename(
    time = Date 
  ) %>%
  mutate(time = mdy_hm(time))
```


```{r, message = FALSE, warning = FALSE}
## load traffic data

traffic_data <- read_csv("Lekagul Sensor Data.csv")

traffic_data_clean <- traffic_data %>%
  rename(
    time = Timestamp
  ) %>%
  mutate(time = ymd_hms(time))
```

Dates to look at:

4/2/16, monitor 6, Methylosmolene
4/9/16, monitor 6, Methylosmolene
8/1/16, monitor 3, Methylosmolene
8/2/16, monitor 2, Chlorodinine
12/2/16, monitor 6, Methylosmolene
12/23/16, monitor 6, Chlorodinine


```{r}
map2 <- readJPEG("Lekagul Roadways labeled v2 copy.jpg") 
```

```{r}

## manually entering in the locations of the factories, which come from "Data Descriptions for Sensor Data.docx", in the Sensor Data file 

## first, manually entering in the factory names

factories <- data.frame(c("Roadrunner", "Kasios", "Radiance", "Indigo"))%>%
  rename(location_name = c..Roadrunner....Kasios....Radiance....Indigo..)

## then, manually entering in the X coordinates

locationsX <- data.frame(c(89, 90, 109, 120)) %>%
  rename(X = c.89..90..109..120.)

## then, manually entering in the Y coordinates

locationsY <- data.frame(c(27, 21, 26, 22)) %>%
  rename(Y = c.27..21..26..22.)

## finally, putting the three columns together so that the rows match up

factory_locations <- cbind(factories, locationsX, locationsY) %>%
  mutate(location_type = "factory")

## manually entering in the locations of the sensors, which come from the "Data Descriptions for Sensor Data.docx", in the Sensor Data file

## first, manually entering in the name of the sensors

name <- data.frame(c("Sensor 1","Sensor 2","Sensor 3","Sensor 4","Sensor 5","Sensor 6","Sensor 7","Sensor 8","Sensor 9")) %>%
  rename(location_name = c..Sensor.1....Sensor.2....Sensor.3....Sensor.4....Sensor.5...)

## next, manually entering in the X locations of each sensor

sensorLocX <- data.frame(c(62, 66, 76, 88, 103, 102, 89, 74, 119)) %>%
  rename(X = c.62..66..76..88..103..102..89..74..119.)

## then, manually entering in the Y locations of each sensor

sensorLocY <- data.frame(c(21, 35, 41, 45, 43, 22, 3, 7, 42)) %>%
  rename(Y = c.21..35..41..45..43..22..3..7..42.)

## finally, putting the three columns together to form a data frame

sensor_locations <- cbind(name, sensorLocX, sensorLocY) %>%
  mutate(location_type = "sensor")

important_locations <-rbind(factory_locations, sensor_locations)
```


```{r}
xlabs <- c(0,25,50,75,100,125,150,175,)

ggplot(important_locations, aes(x = X, y = Y, color = location_type)) +
  background_image(map2) +
  geom_point(size = 2) +
  scale_y_continuous(limits = c(0,200)) +
  scale_x_continuous(limits = c(0,200))

#, breaks = c(0, 200, by = 10), 1
#, breaks = c(0,200, by = 10), 1
#remove breaks

  scale_x_continuous(expand = c(0, 0), 
                     name = NULL,
                     breaks = xlabs,
                     labels = c("1940", "'60", "'80", "2000")
                     ) +
  scale_x_continuous(breaks = round(seq(min(important_locations$x), max(important_locations$x), by = 10),1)) +
  scale_y_continuous(breaks = round(seq(min(important_locations$y), max(important_locations$y), by = 10),1))


  

## -------------------
```

  grid(nx = 5, ny = nx, col = "red", lty = "dotted",
     lwd = par("lwd"), equilogs = TRUE)


#p

plot(1:3)
#grid(10, 5, lwd = par("lwd"), col = "red") # grid only in y-direction

## maybe change the desired number of tick marks:  par(lab = c(mx, my, 7))
op <- par(mfcol = 1:2)
with(important_locations,
     {
     plot(X, Y, col = location_type,
          xlim = c(0, 200), ylim = c(0, 200), panel.first = grid(),
          main = "with(iris,  plot(...., panel.first = grid(), ..) )")
     }
    )
par(op)

```{r}
# adding the camping X and Y coordinates
traffic_data_coord <- traffic_data_clean%>%
  rename(gate_name = `gate-name`)%>%
  mutate(X = ifelse(gate_name == "camping5", 10,
                    ifelse(gate_name == "camping0", 50,
                           ifelse(gate_name== "camping1", 140,
                              ifelse(gate_name=="camping2", 45,
                                     ifelse(gate_name == "camping3", 46,
                                            ifelse(gate_name == "camping4", 48,
                                                   ifelse(gate_name == "camping6",155,
                                                          ifelse(gate_name == "camping7", 190,
                                                                 ifelse(gate_name == "camping8", 195,
                                                                        0))))))))))%>%
  mutate(Y = ifelse(gate_name == "camping5", 75,
                    ifelse(gate_name == "camping0", 160,
                           ifelse(gate_name== "camping1", 155,
                              ifelse(gate_name=="camping2", 140,
                                     ifelse(gate_name == "camping3", 136,
                                            ifelse(gate_name == "camping4", 115,
                                                   ifelse(gate_name == "camping6",20,
                                                          ifelse(gate_name == "camping7", 50,
                                                                 ifelse(gate_name == "camping8", 157,
                                                                        0))))))))))%>%
  mutate(X = ifelse(gate_name == "entrance0", 55,
                  ifelse(gate_name == "entrance1", 9,
                         ifelse(gate_name== "entrance2", 192,
                            ifelse(gate_name=="entrance3", 115,
                                   ifelse(gate_name == "entrance4", 146,
                                                                      0))))))%>%
  mutate(Y = ifelse(gate_name == "entrance0", 196,
                ifelse(gate_name == "entrance1", 136,
                       ifelse(gate_name== "entrance2", 113,
                          ifelse(gate_name=="entrance3", 26,
                                 ifelse(gate_name == "entrance4", 8,
                                                                    0))))))%>%
  mutate(X = ifelse(gate_name == "gate0", 60,
                ifelse(gate_name == "gate1", 55,
                       ifelse(gate_name== "gate2", 20,
                          ifelse(gate_name=="gate3", 153,
                                 ifelse(gate_name == "gate4", 170,
                                        ifelse(gate_name == "gate5", 135,
                                               ifelse(gate_name == "gate6", 117,
                                                      ifelse(gate_name == "gate7", 96,
                                                             ifelse(gate_name == "gate8", 143,
                                                                    0))))))))))%>%
    mutate(Y = ifelse(gate_name == "gate0", 170,
                ifelse(gate_name == "gate1", 160,
                       ifelse(gate_name== "gate2", 150,
                          ifelse(gate_name=="gate3", 143,
                                 ifelse(gate_name == "gate4", 80,
                                        ifelse(gate_name == "gate5", 50,
                                               ifelse(gate_name == "gate6", 45,
                                                      ifelse(gate_name == "gate7", 35,
                                                             ifelse(gate_name == "gate8", 15,
                                                                    0))))))))))%>%
    mutate(X = ifelse(gate_name == "general-gate0", 110,
              ifelse(gate_name == "general-gate1", 60,
                     ifelse(gate_name== "general-gate2", 104,
                        ifelse(gate_name=="general-gate3", 194,
                               ifelse(gate_name == "general-gate4", 65,
                                      ifelse(gate_name == "general-gate5", 130,
                                             ifelse(gate_name == "general-gate6", 140,
                                                    ifelse(gate_name == "general-gate7", 60,
                                                                  0)))))))))%>%
    mutate(Y = ifelse(gate_name == "general-gate0", 199,
            ifelse(gate_name == "general-gate1", 180,
                   ifelse(gate_name== "general-gate2", 170,
                      ifelse(gate_name=="general-gate3", 149,
                             ifelse(gate_name == "general-gate4", 101,
                                    ifelse(gate_name == "general-gate5", 90,
                                           ifelse(gate_name == "general-gate6", 57,
                                                  ifelse(gate_name == "general-gate7", 51,
                                                                0)))))))))

```


```{r}
#adding entrance X coordinates
```

  mutate(Model = ifelse(Stimulus == "426789", "child",
                    ifelse(Stimulus == "426790", "child",
                    ifelse(Stimulus == "426783", "adult",
                    ifelse(Stimulus == "426784", "adult", "no")))))
Camping 5: 10, 75

plot(image_map, axes=FALSE)
grid(5, 5, lwd = 2, col = "red")


```{r}
location_names <- traffic_data_clean%>%
  group_by(`gate-name`)%>%
  summarize(N = n())
```





