---
title: "interactive_map"
output: html_document
---

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(leaflet)
library(lubridate)
library(plotly)
library(jpeg)
library(ggpubr)
```

```{r, warning = FALSE, message = FALSE}
## load sensor data

sensor_data <- read_csv("Sensor Data.csv")

sensor_data_clean <- sensor_data %>%
  rename(
    time = `Date Time`
  ) %>%
  mutate(time = mdy_hm(time))
```


```{r, warning = FALSE, message = FALSE}
## load meteorological data

weather_data <- read_csv("Meteorological Data.csv")

weather_data_clean <- weather_data %>%
  rename(
    time = Date 
  ) %>%
  mutate(time = mdy_hm(time))
```


```{r, message = FALSE, warning = FALSE}
## load traffic data

traffic_data <- read_csv("Lekagul Sensor Data.csv")

traffic_data_clean <- traffic_data %>%
  rename(
    time = Timestamp
  ) %>%
  mutate(time = ymd_hms(time))
```

```{r}
map2 <- readJPEG("Lekagul Roadways labeled v2 copy.jpg") 
```

```{r}

## manually entering in the locations of the factories, which come from "Data Descriptions for Sensor Data.docx", in the Sensor Data file 

## first, manually entering in the factory names

factories <- data.frame(c("Roadrunner", "Kasios", "Radiance", "Indigo"))%>%
  rename(location_name = c..Roadrunner....Kasios....Radiance....Indigo..)

## then, manually entering in the X coordinates

locationsX <- data.frame(c(89, 90, 109, 120)) %>%
  rename(X = c.89..90..109..120.)

## then, manually entering in the Y coordinates

locationsY <- data.frame(c(27, 21, 26, 22)) %>%
  rename(Y = c.27..21..26..22.)

## finally, putting the three columns together so that the rows match up

factory_locations <- cbind(factories, locationsX, locationsY) %>%
  mutate(location_type = "factory")

## manually entering in the locations of the sensors, which come from the "Data Descriptions for Sensor Data.docx", in the Sensor Data file

## first, manually entering in the name of the sensors

name <- data.frame(c(1,2,3,4,5,6,7,8,9)) %>%
  rename(monitor = c.1..2..3..4..5..6..7..8..9.)

## next, manually entering in the X locations of each sensor

sensorLocX <- data.frame(c(62, 66, 76, 88, 103, 102, 89, 74, 119)) %>%
  rename(X = c.62..66..76..88..103..102..89..74..119.)

## then, manually entering in the Y locations of each sensor

sensorLocY <- data.frame(c(21, 35, 41, 45, 43, 22, 3, 7, 42)) %>%
  rename(Y = c.21..35..41..45..43..22..3..7..42.)

## finally, putting the three columns together to form a data frame

sensor_locations <- cbind(name, sensorLocX, sensorLocY) %>%
  mutate(location_type = "sensor")

# important_locations <-rbind(factory_locations, sensor_locations)
```


```{r}
# ggplot(important_locations, aes(x = X, y = Y, color = location_type)) +
 # background_image(map2) +
 # geom_point(size = 2) +
 # scale_y_continuous(limits = c(0,200)) +
 # scale_x_continuous(limits = c(0,200))

#, breaks = c(0, 200, by = 10), 1
#, breaks = c(0,200, by = 10), 1
```

```{r}
# adding the camping X and Y coordinates
traffic_data_coord <- traffic_data_clean%>%
  rename(car_id = `car-id`)%>%
  rename(gate_name = `gate-name`)%>%
  mutate(X = ifelse(gate_name == "camping5", 21,
                    ifelse(gate_name == "camping0", 55,
                           ifelse(gate_name== "camping1", 130,
                              ifelse(gate_name=="camping2", 43,
                                     ifelse(gate_name == "camping3", 43,
                                            ifelse(gate_name == "camping4", 50,
                                                   ifelse(gate_name == "camping6",150,
                                                          ifelse(gate_name == "camping7", 180,
                                                                 ifelse(gate_name == "camping8", 182,                                          
          ifelse(gate_name == "entrance0", 61,
                  ifelse(gate_name == "entrance1", 19,
                         ifelse(gate_name== "entrance2", 182,
                            ifelse(gate_name=="entrance3", 117,
                                   ifelse(gate_name == "entrance4", 140,
          ifelse(gate_name == "gate0", 63,
                ifelse(gate_name == "gate1", 59,
                       ifelse(gate_name== "gate2", 25,
                          ifelse(gate_name=="gate3", 149,
                                 ifelse(gate_name == "gate4", 163,
                                        ifelse(gate_name == "gate5", 132,
                                               ifelse(gate_name == "gate6", 118,
                                                      ifelse(gate_name == "gate7", 97,
                                                             ifelse(gate_name == "gate8", 139
                                                                    ,
          ifelse(gate_name == "general-gate0", 111,
              ifelse(gate_name == "general-gate1", 64,
                     ifelse(gate_name== "general-gate2", 103,
                        ifelse(gate_name=="general-gate3", 185,
                               ifelse(gate_name == "general-gate4", 70,
                                      ifelse(gate_name == "general-gate5", 124,
                                             ifelse(gate_name == "general-gate6", 138,
                                                    ifelse(gate_name == "general-gate7", 65,
                                                      
          ifelse(gate_name == "ranger-base", 128,
              ifelse(gate_name == "ranger-stop0", 90,
                     ifelse(gate_name== "ranger-stop1", 20,
                        ifelse(gate_name=="ranger-stop2", 80,
                               ifelse(gate_name == "ranger-stop3", 148,
                                      ifelse(gate_name == "ranger-stop4", 20,
                                             ifelse(gate_name == "ranger-stop5", 152,
                                                    ifelse(gate_name == "ranger-stop6", 122,
                                                           ifelse(gate_name == "ranger-stop7", 100,                                0)))))))))))))))))))))))))))))))))))))))))%>%
  mutate(Y = ifelse(gate_name == "camping5", 79,
                    ifelse(gate_name == "camping0", 159,
                           ifelse(gate_name== "camping1", 149,
                              ifelse(gate_name=="camping2", 135,
                                     ifelse(gate_name == "camping3", 133,
                                            ifelse(gate_name == "camping4", 110,
                                                   ifelse(gate_name == "camping6",23,
                                                          ifelse(gate_name == "camping7", 55,
                                                                 ifelse(gate_name == "camping8", 151,
                                                                        
          ifelse(gate_name == "entrance0", 185,
                ifelse(gate_name == "entrance1", 131,
                       ifelse(gate_name== "entrance2", 113,
                          ifelse(gate_name=="entrance3", 32,
                                 ifelse(gate_name == "entrance4", 18,
                                        
           ifelse(gate_name == "gate0", 165,
                ifelse(gate_name == "gate1", 155,
                       ifelse(gate_name== "gate2", 145,
                          ifelse(gate_name=="gate3", 140,
                                 ifelse(gate_name == "gate4", 85,
                                        ifelse(gate_name == "gate5", 54,
                                               ifelse(gate_name == "gate6", 48,
                                                      ifelse(gate_name == "gate7", 40,
                                                             ifelse(gate_name == "gate8", 20,
                                                                    
          ifelse(gate_name == "general-gate0", 190,
            ifelse(gate_name == "general-gate1", 173,
                   ifelse(gate_name== "general-gate2", 168,
                      ifelse(gate_name=="general-gate3", 144,
                             ifelse(gate_name == "general-gate4", 101,
                                    ifelse(gate_name == "general-gate5", 88,
                                           ifelse(gate_name == "general-gate6", 62,
                                                  ifelse(gate_name == "general-gate7", 57,
                                                         
          ifelse(gate_name == "ranger-base", 25,
              ifelse(gate_name == "ranger-stop0", 182,
                     ifelse(gate_name== "ranger-stop1", 175,
                        ifelse(gate_name=="ranger-stop2", 163,
                               ifelse(gate_name == "ranger-stop3", 154,
                                      ifelse(gate_name == "ranger-stop4", 105,
                                             ifelse(gate_name == "ranger-stop5", 81,
                                                    ifelse(gate_name == "ranger-stop6", 52,
                                                           ifelse(gate_name == "ranger-stop7", 48,
                                                                      0)))))))))))))))))))))))))))))))))))))))))
```

### The names of the locations and how many times they are repeated 

```{r}
location_names <- traffic_data_clean%>%
  group_by(`gate-name`)%>%
  summarize(N = n())
```

```{r}
sensor_data_w_locations <- sensor_data_clean %>%
   left_join(sensor_locations, by = c("Monitor" = "monitor")) %>%
   select(-location_type)

sensor_data_w_locations %>%
  group_by(X, Y) %>%
  summarize(
    N = n()
  )
```


```{r}
## ggpubr and background_image function ideas and syntax come from code for DC-2 (file entitled dc-2-dataclean.Rmd, submitted by Michelle Flesaker); this code originally came from the following sources ---------------------
## https://rpkgs.datanovia.com/ggpubr/reference/background_image.html
## https://github.com/kassambara/ggpubr/blob/master/R/background_image.R
## https://www.edureka.co/community/58999/add-image-background-to-ggplot
## https://www.engineeringbigdata.com/how-to-add-a-background-image-in-ggplot2-with-r/

 ggplot(sensor_data_w_locations, aes(x = X, y = Y, color = Chemical, size = total_reading)) +
  background_image(map2) +
  geom_jitter(size = 2) +
  scale_y_continuous(limits = c(0,200)) +
  scale_x_continuous(limits = c(0,200))

## this code is directly from Lika Mikhelashvili via Slack 

plot <- sensor_data_w_locations %>%
  plot_ly(
    x = ~X,
    y = ~Y,
    frame = ~hour(time),
    color = ~Reading,
    text = ~paste("Monitor:", Monitor, "\nChemical:", Chemical, "\nReading:", Reading),
    hoverinfo = ~text,
    type = "scatter",
    mode = "markers"
  )

plot

## -------------------
```
# Analyzing the key dates

Dates to look at:

4/2/16, monitor 6, Methylosmolene
4/9/16, monitor 6, Methylosmolene
8/1/16, monitor 3, Methylosmolene
8/2/16, monitor 2, Chlorodinine
12/2/16, monitor 6, Methylosmolene
12/23/16, monitor 6, Chlorodinine


### 2016-04-02

the graph with the grid: 

```{r}
# different colors for different ids not showing up in the legend

data_04_02 <- traffic_data_coord%>%
  filter(year(time) == 2016 & month(time)==04 & day(time) == 02)

data_04_02%>%
  plot_ly(
    x = ~X,
    y = ~Y,
    #ids = ~car_id,
    color = ~factor(car_id),
    frame = ~hour(time),
    text = ~paste("Location:", gate_name, "\nCar ID:", car_id, "\nCar Type:", `car-type`),
    hoverinfo = "text",
    type = 'scatter',
    mode = 'markers'
  )%>%
  layout(title = '2016-04-02',
         
    ## The following code is directly copied and pasted and minimally adapted from users Charlotte Sirot and Maxilmilian Peters on StackOverflow between 10/23/2016 and 2/12/2017 https://stackoverflow.com/questions/40204508/r-plotly-add-a-image-in-background
    ## additional help from https://community.plotly.com/t/add-a-background-image/2457
    
         images = list(
           source = "https://raw.githubusercontent.com/mflesaker/dc-3/master/Lekagul%20Roadways%20labeled%20v2%20copy.jpg",
        xref = "x",
        yref = "y",
        x = 0,
        y = 200,
        sizex = 200,
        sizey = 200,
        sizing = "stretch",
        opacity = 1,
        layer = "below"
         ),
    ## ----------------------------------------
    
    ## This code is directly from https://plotly.com/r/setting-graph-size/ --------- with adjustments made for width and height
    autosize = F,
    width = 620,
    height = 500,
    ## --------
    
    ## This code is directly from https://plotly.com/r/reference/layout/xaxis/ -----
    xaxis = list(
      tickmode = 'linear',
           tick0 = 0,
      dtick = 20
         ),
    yaxis = list(
      tickmode = 'linear',
           tick0 = 0,
      dtick = 20
      ##------
         )
    )

```


General graph without the grid:
```{r}
anim_graph <- function(my_year, my_month, my_day){
  dataname <- traffic_data_coord%>%
  filter(year(time) == my_year & month(time)==my_month & day(time) == my_day)
  
  plot <- dataname%>%
    plot_ly(
    x = ~X,
    y = ~Y,
    #ids = ~car_id,
    color = ~factor(car_id),
    frame = ~hour(time),
    text = ~paste("Location:", gate_name, "\nCar ID:", car_id, "\nCar Type:", `car-type`),
    hoverinfo = "text",
    type = 'scatter',
    mode = 'markers',
    
    ## code from https://plotly.com/r/setting-graph-size/ --------
    
    width = 620,
    height = 500
    
    ## ----
  )%>%
  layout(title = paste(my_year, "/", my_month, "/", my_day),
         images = list(
           source = "https://raw.githubusercontent.com/mflesaker/dc-3/master/Lekagul%20Roadways%20labeled%20v2%20copy.jpg",
        xref = "x",
        yref = "y",
        x = 0,
        y = 200,
        sizex = 200,
        sizey = 200,
        sizing = "stretch",
        opacity = 1,
        layer = "below"
         ))
    ## --------
    

}
```
----
Setting grid code:

     ##This code is directly from https://plotly.com/r/reference/layout/xaxis/ -----
    xaxis = list(
      tickmode = 'linear',
           tick0 = 0,
      dtick = 20
         ),
    yaxis = list(
      tickmode = 'linear',
           tick0 = 0,
      dtick = 20))
  

  ----

4/2/16, monitor 6, Methylosmolene

4/9/16, monitor 6, Methylosmolene

8/1/16, monitor 3, Methylosmolene

8/2/16, monitor 2, Chlorodinine

12/2/16, monitor 6, Methylosmolene

12/23/16, monitor 6, Chlorodinine


```{r}
graph_04_02 <- anim_graph(2016, 04, 02)
  graph_04_02
```

```{r}
graph_04_09 <- anim_graph(2016, 04, 09)
graph_04_09
```

**No records for 08/02, 12/02, 12/23**


# Tracking car id 's

"20151112031119-409"

"20155201025245-696"

"20152824032830-251"

"20150416040441-902"

"20152925022919-735"

"20154907044911-419"

"20150204100226-134"

"20160623090611-424"

"20153427103455-30"

```{r}
# How to add gate name in the hover info
# how to add background image

tracking_cars <- function(id){
  p <- traffic_data_coord%>%
  filter(car_id == id)%>%
  plot_ly(
    x = ~X,
    y = ~Y,
    ids = ~factor(car_id),
    frame = ~factor(time),
    text = ~paste("Location:", gate_name, "\nCar ID:", car_id, "\nCar Type:", `car-type`),
    hoverinfo = "text",
    type = 'scatter',
    mode = 'markers',
    width = 620,
    height = 500
  )%>%   
  layout(title = paste("Car ID:", id),
        images = list(
        source = "https://raw.githubusercontent.com/mflesaker/dc-3/master/Lekagul%20Roadways%20labeled%20v2%20copy.jpg",
        xref = "x",
        yref = "y",
        x = 0,
        y = 200,
        sizex = 200,
        sizey = 200,
        sizing = "stretch",
        opacity = 1,
        layer = "below"
         ),
        
        ## x and y axis fixed code from https://plotly.com/r/axes/
        xaxis = list(range = c(0, 200)),
        yaxis = list(range = c(0, 200))
        ## ------
        )
  
  p
}
```


```{r}
tracking_cars("20151112031119-409")
tracking_cars("20155201025245-696")
tracking_cars("20152824032830-251")
tracking_cars("20150416040441-902")
tracking_cars("20152925022919-735")
tracking_cars("20154907044911-419")
tracking_cars("20150204100226-134")
tracking_cars("20160623090611-424")
tracking_cars("20153427103455-30")

```

